\section{Prototype Relabeling Vulnerability in kNN}
\label{sec:problem}

Let $S=((z_1,y_1),\ldots,(z_n,y_n))$ be an ordered labeled sample in a metric space $(\mathcal X,d)$, with labels in a finite set $\mathcal Y$.  A deterministic kNN classifier orders training occurrences by distance to a query $x$ and then by a fixed tie-breaking rule.  The prediction $h_{S,k}(x)$ is the majority label among the first $k$ occurrences, with deterministic tie-breaking among labels.

\subsection{LOO is an error-estimation diagnostic}

For a training occurrence $i$, LOO removes that occurrence and evaluates the deleted point:
\[
    I^{\mathrm{LOO}}_{i,k}(S)
    =
    \mathbf 1\{h_{S\setminus i,k}(z_i)\ne y_i\}.
\]
This is a useful small-sample error-estimation device.  It answers whether $z_i$ is correctly recovered by the remaining prototypes.  It does not ask whether changing the prototype at index $i$ changes predictions at other query points.

\subsection{Fixed-location relabeling vulnerability}

Let $S^{i\leftarrow (z_i,y')}$ denote the sample obtained by changing the label of occurrence $i$ while keeping its location fixed.  For a query $x$, define the fixed-location relabeling vulnerability indicator
\[
    V_{i,k}(S,x)
    =
    \mathbf 1\{\exists y'\ne y_i:
    h_{S^{i\leftarrow (z_i,y')},k}(x)\ne h_{S,k}(x)\}.
\]
The query-level vulnerability is
\[
    V_k(S,x)=\max_i V_{i,k}(S,x),
\]
and the exact enumerated vulnerability rate on an evaluation set $Q$ is
\[
    \mathrm{EnumVulnRate}_k(S,Q)
    =
    \frac{1}{|Q|}\sum_{x\in Q} V_k(S,x).
\]
Let $\mathcal Y_{\mathrm{rep}}(S,i)$ denote the admissible replacement-label set for prototype $i$.  In the main theory, any label in $\mathcal Y\setminus\{y_i\}$ is admissible.  In the experiments, admissible labels are restricted to the class labels observed in the current training split, excluding $y_i$.  For geometric replacement, the candidate may also move in feature space.  The present results are exact for fixed-location one-label relabeling under deterministic voting; when the location also changes, the same margin band should be treated only as a heuristic first-pass screen because the top-$k$ neighborhood itself may change.

\begin{table}[t]
\centering
\small
\begin{tabularx}{\linewidth}{@{}YYY@{}}
\toprule
Quantity & Question answered & Role in this paper \\
\midrule
LOO indicator & Is the deleted occurrence recovered by the remaining prototypes? & Error-estimation signal \\
PRV / $\mathrm{EnumVulnRate}_k$ & Can relabeling one retained prototype alter a query prediction? & Prototype-reliability signal \\
Local vote margin/gap & How far is the local vote from a decision change? & Efficient audit statistic \\
\bottomrule
\end{tabularx}
\caption{LOO and fixed-location relabeling vulnerability answer different reliability questions.}
\label{tab:paa-notions}
\end{table}
